Titeln på avhandlingens språk

### 2023-01-30 body/part1/background.tex
edge computing

The architecture of edge computing offers several advantages.
Thanks to their proximity to users, cloudlets can serve highly latency-sensitive and resource-intensive applications with extremely low latencies while still providing orders of magnitude more computing and energy resources than those present on mobile and wearable devices.
Mobile \gls{XR}, such as \gls{WCA}~\cite{ha2014towards,chen2018application,wang2020scaling,chen2017empirical,chen2018application}, and 5G-enabled \glspl{CPS} and \glspl{NCS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient} are uniquely poised to take advantage of this characteristic of edge computing.

>>>>

The architecture of edge computing offers several advantages.
Thanks to their proximity to users, cloudlets can serve highly latency-sensitive and resource-intensive applications with extremely low latencies while still providing orders of magnitude more computing and energy resources than those present on mobile and wearable devices.
Mobile \gls{XR}, such as \gls{WCA}~\cite{ha2014towards,chen2018application,wang2020scaling,chen2017empirical,chen2018application}, and 5G-enabled \glspl{CPS} and \glspl{NCS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient} are uniquely poised to take advantage of these characteristic of edge computing.
By processing and aggregating data closer to where its needed, cloudlets can also drastically reduce the amount of traffic going to cloud datacenters.
Cloudlets also present opportunities for increased data security, privacy, and integrity, by keeping it geographically close to its origin and by allowing for anonymization through denaturing and local aggregation before offloading to cloud services~\cite{satyanarayanan2017emergence}.
